%
% File proposal-team53.tex
%
%% Based on the style files for EMNLP 2020, which were
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2021}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

\aclfinalcopy
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

% Content lightly modified from original work by Jesse Dodge and Noah Smith


\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{
  Project Proposal \\
  CS598 DL4H Spring 2023
  }

\author{Shiyu (Sherry) Li and Wei-Lun (Will) Tsai \\
  \texttt{\{shiyuli2, wltsai2\}@illinois.edu}
  \\[2em]
  Group ID: 53\\
  Paper ID: 28\\
  Presentation link: \url{\#TODO} \\
  Code link: \url{https://github.com/willtsai/dlh-sp23-team53}} 

\begin{document}
\maketitle

% All sections are mandatory.
% Keep in mind that your page limit is 8, excluding references.
% For specific grading rubrics, please see the project instruction.

\section{Cite the original paper.}
The paper we have selected for our reproducibility study is: 
\textit{Context-aware Health Event Prediction via Transition 
Functions on Dynamic Disease Graphs} \cite{chet}

\section{State the general problem the paper aims to solve. Do not
use the same language as the paper.}
The authors of the paper propose a new deep learning model called Chet
(\textbf{c}ontext-aware \textbf{h}ealth \textbf{e}vent prediction via
\textbf{t}ransition functions on dynamic disease graphs) that leverages the
relationship between diseases and how they develop over time to predict future
outcomes and diagnoses. Existing research on deep learning models for
classification and prediction of diseases based on longitudinal EHR data have
modeled disease diagnoses as independent events in their respective visits.
However, intuition and data indicate that there are in fact hidden patterns
within the combinations of disease diagnoses that may be useful for predicting
future outcomes for patients, but yet have not been leveraged in existing
best-in-class healthcare deep learning models. The Chet model is able to learn
how diagnosed diseases develop over the course of each patient's doctor visits
and then utilize this learned disease combination context to predict future
outcomes and diagnoses. 

\section{Describe the new and specific approach taken by the
paper. Discuss why it is interesting or innovative.}
Instead of treating diagnosis as independent diseases as most existing approaches,
this paper tried to view disease diagnosis as co-dependent events and use these
combinational and dynamic disease information to inform the deep learning model and make it  
context-aware. The most innovative part of the approach is the design to include both
disease combinational information and the dynamic scheme of disease into the model. To include 
disease combinational information, the paper constructed a weighted disease combination
based on the entire longitudinal EHR data globally and also a disease subgraph based on the 
specific visit locally. To include dynamic scheme of diseases, the paper utilized a disease-level
temporal learning with multiple diagnosis roles and corresponding transition functions to extract
historical contexts.

\section{Identify the specific hypotheses you plan to verify in your
reproduction study.}
In our reproduction study, we will use the same methodology as proposed by the
authors for data selection, cleaning, and preprocessing as the authors of the
paper. Specifically, we will join the MIMIC-III \cite{mimic3} and MIMIC-IV
\cite{mimic4} datasets along the same overlapping time ranges that the authors
describe and split training/validation/test sets randomly using the same ratios
they used. We will build the diagnosis graphs and calculate the adjacency
matrices for their corresponding subgraphs using the same methodology described
by the authors. Leveraging the same parameter settings specified, we will train
the model and then compare the performance of the Chet model to the listed
baseline performance of best-in-class models for diagnosis prediction and heart
failure prediction. We will not attempt to reproduce the baseline performance of
best-in-class models.

\section{Outline any additional ablations you plan to do and
explain why they are interesting.}
As an initial proposal, we are interested in the following four potential ablation studies. We will at least complete one. Additional ones
will be tried if we have enough capacity.

\begin{itemize}
  \item Removing the dynamic part of GNN. This ablation study is mentioned in the paper with few details. This ablation study is interesting 
  because dynamic subgraph is used for building local context of visits in the model. Removing this part will only leave global combination
  graph in GNN, and by comparing this variant with the original Chet, it will help us understand the effect of dynamic subgraphs.
  \item Removing  the transition functions. This ablation study is mentioned in the paper with few details. This ablation study is interesting 
  because transition functions are used for extracting historical contexts for each diagnosis roles to learn transition process of diseases. By 
  comparing this variant with the original Chet, it will help us understand the effect of these transition functions.
  \item Removing attention from embedding layer. At the last layer of the model, the paper applied a location-based attention to calculate the 
  final patient embedding of all visits. By comparing this variant with the original Chet, it will help us understand the effect of the attention
  used in the embedding layer.
  \item Reduce three diagnosis roles and three corresponding transition functions to two. When doing diagnosis-level temporal learning, the paper 
  defined three diagnosis roles and used three corresponding transition functions. We want to try to reduce to two to better understand the importance
  of these diagnosis roles.
\end{itemize}

\section{Explain how you have access to the necessary data.}
For their experiment, the authors use the MIMIC-III \cite{mimic3} and MIMIC-IV
\cite{mimic4} datasets for training, validation, and testing. Since we have
completed the required training and are credentialed users, we are able to
download both the MIMIC-III and MIMIC-IV datasets from PhysioNet
\cite{physionet}.

\section{Discuss the computational feasibility of your proposed work.}
We have downloaded the data to our local machine and used the author's 
original \href{https://github.com/LuChang-CS/Chet}{code base} to test 
the computational feasibility. Based on our initial investigation, 
it took around 10 minutes for data preprocessing and 96 hours to complete 
total 200 epoches of training for the training set. These are definitely
long-running tasks but still feasible with our current resource. But we might
slightly reduce the size of dataset or the epoch iteration numbers during actual training
for our ablation studies depends on our capacity.


\section{Specify if you will be re-using existing code and provide a link to it,
or if you will implement the code yourself.}
We plan to re-use the existing code provided by the authors of the paper for
data preprocessing, building the needed input graphs/matrices, building the
model architecture, and training the model for the experiment. We will author
our own shell scripts to download, unzip, and move datasets into the appropriate
paths. We also plan to evelop our own code to compute and evaluate model
performance based on the test dataset following the metrics and methodology
detailed in the paper, as well as make the required modifications to the
existing model architecture and training code to perform the ablation studies
mentioned in the paper as well as our own extra ablations. The code provided by
the authors is available at \url {www.github.com/LuChang-CS/Chet}
\cite{chet}, we will clone this as reference for our implementations described
above.

\bibliographystyle{acl_natbib}
\bibliography{dl4h-sp23-project-team53}

%\appendix



\end{document}

% \section{Introduction} \# TODO: A  few  sentences  placing  the  work  in
% context. Limit it to a few paragraphs at most; your report is on reproducing a
% piece of work, you don’t have to motivate that work. However, it should be
% clear enough what the original paper is about and what the contribution of it
% is.

% \section{Scope of reproducibility} \# TODO: Explain the claims from the paper
% you picked for the reproduction study and briefly motivate your choice. We
% recommend picking the claim that is the central contribution of the paper. To
% find what this contribution is, try to summarize the most important result of
% the paper in 1-2 sentences, e.g. ``This paper introduces a new activation
% function X that outperforms a similar activation function Y on tasks Z,V,W.'' 

% Make the scope as specific as possible. It should be something that can be
% supported or rejected by your data. For example, consider this scope: 

% \textit{``Contextual embedding models have shown strong performance on a
% number of tasks across NLP. We will run experiments evaluating two types of
% contextual embedding models on datasets X, Y, and Z.''}


% That scope is too broad and lacks precise outcome (what is ``strong
% performance?''). Now consider this scope:

% \textit{``Finetuning pretrained BERT on SST-2 will have higher accuracy than
% an LSTM trained with GloVe embeddings.''}

% This scope is better because it's more specific and has an outcome that can be
% either supported or rejected based on your work.

% \subsection{Addressed claims from the original paper} \# TODO: Clearly itemize
% the claims you are testing: \begin{itemize} \item Claim 1 \item Claim 2 \item
% Claim 3 \end{itemize}


% \section{Methodology} \# TODO: In this section you explain your approach --
% did you use the author's code, did you aim to re-implement the approach from
% the paper description? Summarize the resources (code, documentation, GPUs)
% that you used. 

% \subsection{Model descriptions} \# TODO: Describe the models used in the
% original paper, including the architecture, learning objective and the number
% of parameters.

% \subsection{Data descriptions} \# TODO: Describe the datasets you used (with
% some statistics) and how you obtained them. 

% \subsection{Hyperparameters} \# TODO: Describe how you set the hyperparameters
% and what the source was for their value (e.g. paper, code or your guess). 

% \subsection{Implementation} \# TODO: Describe whether you use the existing
% code or write your own code, with the link to the code. Note that the github
% repo you link to should be public and have a clear documentation.

% \subsection{Computational requirements} \# TODO: Provide information on
% computational requirements for each of your experiments. For example, the
% number of CPU/GPU hours and memory requirements. Mention both your estimation
% made before running the experiments (i.e. in the proposal) and the actual
% resources you used to reproducing the experiments. \textbf{\textit{You'll need
% to think about this ahead of time, and write your code in a way that captures
% this information so you can later add it to this section.} }

% \section{Results} \# TODO: Start with a high-level overview of your results.
% Does your work support the claims you listed in section 2.1? Keep this section
% as factual and precise as possible, reserve your judgement and discussion
% points for the next ``Discussion'' section. 

% Go into each individual result you have, say how it relates to one of the
% claims, and explain what your result is. Logically group related results into
% sections. Clearly state if you have gone beyond the original paper to run
% additional experiments and how they relate to the original claims. 

% Tips 1: Be specific and use precise language, e.g. ``we reproduced the
% accuracy to within 1\% of reported value, that upholds the paper's conclusion
% that it performs much better than baselines.'' Getting exactly the same number
% is in most cases infeasible, so you'll need to use your judgement call to
% decide if your results support the original claim of the paper. 

% Tips 2: You may want to use tables and figures to demonstrate your results.

% % The number of subsections for results should be the same as the number of
% hypotheses you are trying to verify.

% \subsection{Result 1} \# TODO:

% \subsection{Result 2} \# TODO:

% \subsection{Additional results not present in the original paper} \# TODO:
% Describe any additional experiments beyond the original paper. This could
% include experimenting with additional datasets, exploring different methods,
% running more ablations, or tuning the hyperparameters. For each additional
% experiment, clearly describe which experiment you conducted, its result, and
% discussions (e.g. what is the indication of the result).

% \section{Discussion} \# TODO: Describe larger implications of the experimental
% results, whether the original paper was reproducible, and if it wasn’t, what
% factors made it irreproducible. 

% Give your judgement on if you feel the evidence you got from running the code
% supports the claims of the paper. Discuss the strengths and weaknesses of your
% approach -- perhaps you didn't have time to run all the experiments, or
% perhaps you did additional experiments that further strengthened the claims in
% the paper.

% \subsection{What was easy} \# TODO: Describe which parts of your reproduction
% study were easy. E.g. was it easy to run the author's code, or easy to
% re-implement their method based on the description in the paper. The goal of
% this section is to summarize to the reader which parts of the original paper
% they could easily apply to their problem. 

% Tips: Be careful not to give sweeping generalizations. Something that is easy
% for you might be difficult to others. Put what was easy in context and explain
% why it was easy (e.g. code had extensive API documentation and a lot of
% examples that matched experiments in papers). 

% \subsection{What was difficult} \# TODO: Describe which parts of your
% reproduction study were difficult or took much more time than you expected.
% Perhaps the data was not available and you couldn't verify some experiments,
% or the author's code was broken and had to be debugged first. Or, perhaps some
% experiments just take too much time/resources to run and you couldn't verify
% them. The purpose of this section is to indicate to the reader which parts of
% the original paper are either difficult to re-use, or require a significant
% amount of work and resources to verify. 

% Tips: Be careful to put your discussion in context. For example, don't say
% ``the math was difficult to follow,'' say ``the math requires advanced
% knowledge of calculus to follow.'' 

% \subsection{Recommendations for reproducibility} \# TODO: Describe a set of
% recommendations to the original authors or others who work in this area for
% improving reproducibility.

% \section{Communication with original authors} \# TODO: Document the extent of
% (or lack of) communication with the original authors. To make sure the
% reproducibility report is a fair assessment of the original research we
% recommend getting in touch with the original authors. You can ask authors
% specific questions, or if you don't have any questions you can send them the
% full report to get their feedback.
